---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(RedisBaseContainer)


if(FALSE){
  library(readr)
  fileName <- "vignettes/vignette.md"
  knitr::knit("inst/vignette.Rmd", output = fileName)
  fileName <- fileName
  content <- readChar(fileName, file.info(fileName)$size)
  content <- gsub("---.+?---","",content)
  content <- gsub("^(\r\n)+","",content)
  write_file(content, file = "README.md")
  file.rename(fileName, "vignettes/vignette.Rmd")
}
```


This package is an extension package for the `DockerParallel` package and defines the common functions for the container class. It cannot be directly used by the end user. The user should use the package `doRedisContainer` and `RedisParamContainer`.

# doRedisContainer
The package `doRedisContainer` provides the worker container with foreach doRedis backend.At the time of writing, the package `doRedis` is not available on CRAN, the latest version can be installed from github `remotes::install_github("bwlewis/doRedis")`. The worker container can be made by
```{r}
library(doRedisContainer)
workerContainer <- doRedisWorkerContainer(image = "r-base")
workerContainer
```
The argument `image` determines the base image used by the container. The server container can be obtained by
```{r}
serverContainer <- doRedisServerContainer()
serverContainer
```

# RedisParamContainer
The package `RedisParamContainer` provides the worker container with BiocParallel RedisParam backend. At the time of writing, the package `RedisParam` is not available on Bioconductor, the latest version can be installed from github `remotes::install_github("mtmorgan/RedisParam")`. The worker container can be made by
```{r}
library(RedisParamContainer)
workerContainer <- RedisParamWorkerContainer(image = "r-base")
workerContainer
```
The argument `image` determines the base image used by the container. The server container can be obtained by
```{r}
serverContainer <- RedisParamServerContainer()
serverContainer
```
